Supporting information: Copulas and their potential for ecology

### 2019-09-22 Paper.Rmd
edits suggested by Shyamolina made

\begin{figure}[!h]
\begin{center}
\includegraphics[width=\textwidth]{./Results/PedagogSuppMat_Normal.pdf}
\caption[Example normal copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example normal copulas. 
S is Spearman correlation; $p$ is the value of the parameter for the normal
family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, respectively (see Background section for definition). The 
parameter range for the family is $p \in [-1,1]$, and lower- and upper-tail
dependence are always $0$.\label{figped_N}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=\textwidth]{./Results/PedagogSuppMat_Clayton.pdf}
\caption[Example Clayton copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Clayton  
copulas. S is Spearman correlation; $p$ is the value of the parameter for the Clayton family (it 
is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, 
respectively (see Background section for definition). The parameter range for the family is $p \in (0,\infty)$, lower-tail dependence is $2^{-1/p}$ and upper-tail
dependence is $0$.\label{figped_C}}
\end{center}
\end{figure}

@@

<!--***SHYAMOLINA: Please do the following to help me revise this section, so far only covering changes in the presentation of the bivariate results. Please let me know if any of this is unclear or you want to discuss anything.
1) Replace the pithy abbreviations for the different copulas (N, C, SC, G, etc.) with their full names throughout the main text and sup mat, including in figure and table captions. This will not affect BB1, BB6, etc., but it will affect SBB1, SBB6, etc., which will now be called survival BB1, survival BB6, etc.

>>>> Done. I don't know whether it should be called as a Normal copula or an Normal copula? Now, we use "an".

2) Add AIC and BIC columsn to table S3, and all analogous figures (e.g., S5, S7, S9, etc). Also reduce the number of digits shown after the decimal to 2 for AIC and BIC and 4 for the other columns.
3) Sort the rows of Table S3 (and all analogous tables, e.g., S5, S7, etc.) by AIC, putting the lowest AIC at the top. This should mean the highest AICw is also at the top.

>>>> Added, sorting based on min AIC.

3) Move Table S3 to an appropriate place in the main text. Choose the place based on where it is first cited in the main text. Same for Fig. S21 and Table S4.
7) Combine tables S6, S8, S10 into one table, and fix it so
whenever we currently cite one of those, change it so we cite the combined table instead.
8) Put the cor results only, for Spearman only (or is Kendall more consistent with what we do elsewhere - what do you think?) from tables S4, S6, S8, S10 into Table 2 as a new row.

>>>> All done.
-->

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=\textwidth]{./Results/PedagogSuppMat_Normal.pdf}
\caption[Example normal copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example normal copulas. 
K is Kendall correlation; $p$ is the value of the parameter for the normal
family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, respectively (see Background section for definition). The 
parameter range for the family is $p \in [-1,1]$, and lower- and upper-tail
dependence are always $0$.\label{figped_N}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=\textwidth]{./Results/PedagogSuppMat_Clayton.pdf}
\caption[Example Clayton copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Clayton  
copulas. K is Kendall correlation; $p$ is the value of the parameter for the Clayton family (it 
is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, 
respectively (see Background section for definition). The parameter range for the family is $p \in (0,\infty)$, lower-tail dependence is $2^{-1/p}$ and upper-tail
dependence is $0$.\label{figped_C}}
\end{center}
\end{figure}

@@

<!--***SHYAMOLINA: Please do the following to help me revise this section, so far only covering changes in the presentation of the bivariate results. Please let me know if any of this is unclear or you want to discuss anything.
1) Replace the pithy abbreviations for the different copulas (N, C, SC, G, etc.) with their full names throughout the main text and sup mat, including in figure and table captions. This will not affect BB1, BB6, etc., but it will affect SBB1, SBB6, etc., which will now be called survival BB1, survival BB6, etc.
>>>> Done. I don't know whether it should be called as a Normal copula or an Normal copula? Now, we use "an".
2) Add AIC and BIC columsn to table S3, and all analogous figures (e.g., S5, S7, S9, etc). Also reduce the number of digits shown after the decimal to 2 for AIC and BIC and 4 for the other columns.
3) Sort the rows of Table S3 (and all analogous tables, e.g., S5, S7, etc.) by AIC, putting the lowest AIC at the top. This should mean the highest AICw is also at the top.
>>>> Added, sorting based on min AIC.
3) Move Table S3 to an appropriate place in the main text. Choose the place based on where it is first cited in the main text. Same for Fig. S21 and Table S4.
7) Combine tables S6, S8, S10 into one table, and fix it so
whenever we currently cite one of those, change it so we cite the combined table instead.
8) Put the cor results only, for Spearman only (or is Kendall more consistent with what we do elsewhere - what do you think?) from tables S4, S6, S8, S10 into Table 2 as a new row.
>>>> All done.
-->

### 2019-09-22 SupportingInformation.Rmd
edits suggested by Shyamolina made

<!--Now the copula figures that were not presented in the main text-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvClayton.pdf}
\caption[Example survival Clayton copulas]{Log-transformed pdfs (A-E) and samples (F-J) 
from example survival Clayton 
copulas. S is Spearman correlation; p is the value of the parameter for the survival Clayton 
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in (0,\infty)$, upper-tail dependence is $2^{-1/p}$ and lower-tail
dependence is $0$.\label{figped_SC}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Gumbel.pdf}
\caption[Example Gumbel copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Gumbel copulas. S is 
Spearman correlation; $p$ is the value of the parameter for the Gumbel family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in [1,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $2-2^{1/p}$.\label{figped_G}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvGumbel.pdf}
\caption[Example survival Gumbel copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example survival Gumbel 
copulas. S is Spearman correlation; $p$ is the value of the parameter for the survival Gumbel 
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in [1,\infty)$, upper-tail dependence is $0$ and lower-tail
dependence is $2-2^{1/p}$.\label{figped_SG}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvJoe.pdf}
\caption[Example survival Joe copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example survival Joe  
copulas. K is Spearman correlation; $p$ is the value of the parameter for the survival Joe  
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in [1,\infty)$, upper-tail dependence is $0$ and lower-tail
dependence is $2-2^{1/p}$.\label{figped_SJ}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Frank.pdf}
\caption[Example Frank copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Frank copulas. S is Kendall correlation; $p$ is the value of the parameter for the Frank family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in (0,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $0$.\label{figped_F}}
\end{center}
\end{figure}

>>>>

<!--Now the copula figures that were not presented in the main text-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvClayton.pdf}
\caption[Example survival Clayton copulas]{Log-transformed pdfs (A-E) and samples (F-J) 
from example survival Clayton 
copulas. K is Kendall correlation; p is the value of the parameter for the survival Clayton 
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in (0,\infty)$, upper-tail dependence is $2^{-1/p}$ and lower-tail
dependence is $0$.\label{figped_SC}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Gumbel.pdf}
\caption[Example Gumbel copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Gumbel copulas. K is Kendall 
correlation; $p$ is the value of the parameter for the Gumbel family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in [1,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $2-2^{1/p}$.\label{figped_G}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvGumbel.pdf}
\caption[Example survival Gumbel copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example survival Gumbel 
copulas. K is Kendall correlation; $p$ is the value of the parameter for the survival Gumbel 
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in [1,\infty)$, upper-tail dependence is $0$ and lower-tail
dependence is $2-2^{1/p}$.\label{figped_SG}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvJoe.pdf}
\caption[Example survival Joe copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example survival Joe  
copulas. K is Kendall correlation; $p$ is the value of the parameter for the survival Joe  
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in [1,\infty)$, upper-tail dependence is $0$ and lower-tail
dependence is $2-2^{1/p}$.\label{figped_SJ}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Frank.pdf}
\caption[Example Frank copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Frank copulas. K is Kendall correlation; $p$ is the value of the parameter for the Frank family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in (0,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $0$.\label{figped_F}}
\end{center}
\end{figure}
